---
title: "Project Proposal"
author: "Regression Rockstars - James Cai, Steph Reinke, Sarah Wu, Michael Zhou"
format: pdf
execute: 
  warning: false
  message: false
  echo: false
editor: visual
---

```{r}
#| label: load-pkg-data
#| warning: false
#| message: false

library(tidyverse)
library(tidymodels)
library(knitr) 
library(patchwork)

scoobydoo <- read_csv("data/Scooby-Doo Completed.csv")
```

## Introduction

Scooby-Doo is a popular animated TV show that follows a group of teenagers and a talking Great Dane, Scooby-Doo, as they solve mysteries involving supernatural monsters and creatures. Each episodes typically involves seeking and scheming to find the villain, ending with a dramatic unmasking of the monster. The show focuses on themes of friendship and teamwork. The show aired on CBS from 1969 - 1976, but there has been many subseries and reboots.

We are interested in researching Scoody-Doo IMBD ratings because we all enjoyed Scooby-Doo in our childhoods. We also think that finding certain predictors of animated TV series ratings is useful for the entertainment industry. Specifically, our findings could be useful to anyone looking to create an animated TV series and wanting to know what aspects make up a successful episode. If Scooby-Doo continues to create spin off shows, this information could inform their future episodes as well--what elements of the show tend to receive better responded and a higher IMBD rating?

Our primary research question is what factors explain the variability in the IMBD scores of Scooby-Doo episodes?

We want to investigate how monster_amount, engagement, and who unmasked the villain (unmask_fred, and so on for all the main group) adequately explain the variability of the IMBD rating. We think that the more monsters the better the rating will be, because we think there is more action and suspense in episodes with more monsters. We also think that the higher engagement the worse the rating will be, because we think that people are more likely to write a review online when they do not like something than if they do. We think that episodes where Fred unmasked the villian will have a higher rating because we think that he is the leader of the group and thus, we think that people will be more drawn to him.

## Data description

The Scooby-Doo data was found on the [TidyTuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-13/readme.md#scooby-doo-episodes) database on Github. The data originally comes from [Kaggle](https://www.kaggle.com/datasets/williamschooleman/scoobydoo-complete) and was manually aggregated by user [Plummye](https://www.kaggle.com/williamschooleman) in 2021. The curator took roughly one year to watch every Scooby-Doo iteration and track every variable in this dataset. It is noted that some of the values are subjective by nature of watching, but the original data data curator tried to keep the data collection consistent across the different episodes.

Each observation is an episode from a rendition of the Scooby-Doo franchise up until February 25, 2021, including movies and specials. The variables that were measured include the series and episode name, engagement, IMDB score, and many details about what happens in each episode itself, such as how many monsters appeared, which character captures and unmasks them, and more.

## Initial exploratory data analysis

```{r response-dist}
#| warning: false
#| message: false

scoobydoo <- scoobydoo |>
  mutate(imdb = as.numeric(imdb))

p1 <- scoobydoo |>
  ggplot(aes(x = imdb)) +
  geom_histogram() +
  labs(x = "IMDB score",
       y = "Frequency",
       title = "IMDB Score") +
  theme_minimal()
```

```{r qualpred-dist}
#| warning: false
#| message: false

p2 <- scoobydoo |>
  ggplot(aes(x = monster.amount)) +
  geom_histogram(bins=7) +
  labs(x = "Number of Monsters",
       y = "Frequency",
       title = "Number of Monsters") +
  theme_minimal()
```

```{r patchwork}
#| warning: false
#| message: false

p1 | p2
```

The distribution of IMDB scores is unimodal, roughly symmetrical and has a range from 4 to 10.

The distribution of the number of monsters is right skewed with a center around 0.

```{r catpred-dist}

scoobydoo |>
  ggplot(aes(x = network)) +
  geom_bar() +
  coord_flip() +
  labs(x = "Network Aired On",
       y = "Frequency",
       title = "Network Aired On") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

The distribution of Networks aired on shows that there is a clear majority with ABC.

```{r qual}
#| warning: false

scoobydoo |>
  ggplot(aes(x = monster.amount, y = imdb)) +
  geom_point() +
  labs(x = "Number of Monsters",
       y = "IMDB rating",
       title = "Number of Monsters and IMDB Rating") +
  theme_minimal()
```

```{r cat}
#| warning: false
#| message: false

scoobydoo |>
  ggplot(aes(x = network, y = imdb)) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "Network Aired On",
       y = "IMDB rating",
       title = "Network Aired On and IMDB Rating") +
  theme_minimal()
```

```{r interact}
#| warning: false

scoobydoo |>
  ggplot(aes(x = monster.amount, y = imdb, color = network)) +
  geom_point() +
  labs(x = "Number of Monsters",
       y = "IMDB rating",
       title = "Number of Monsters and IMDB Rating") +
  theme_minimal()
```

## Analysis approach

We are planning to use three potential predictors: monster_amount, a quantitative variable for the number of monster in the episode; engagement, a quantative variable for the number of reviews on IMDB for an episode; and villain_unmask, a categorical variable that takes the value Fred, Daphnie, Velma, Shaggy, and Scooby for the character who unmasks the villain, to predict the IMDB score of each episode, which obviously is a quantitative variable.

We plan to use multiple linear regression for analyze the data.

## Data dictionary

The data dictionary can be found [here](data/README.md).
