---
title: "Analyzing IMBD Scores of Scooby-Doo Episodes"
author: "Regression Rockstars: James Cai, Steph Reinke, Sarah Wu, Michael Zhou"
date: "November 16, 2023"
format: pdf
execute: 
  warning: false
  message: false
  echo: false
editor: visual
---

```{r}
#| label: load-pkg-data
#| warning: false
#| message: false

library(tidyverse)
library(tidymodels)
library(knitr) 
library(patchwork)
library(skimr)

scoobydoo <- read_csv("data/Scooby-Doo Completed.csv")
```

# Introduction and Data:

## Introduction

Scooby-Doo is a popular animated TV show that follows a group of teenagers and a talking Great Dane, Scooby-Doo, as they solve mysteries involving supernatural monsters and creatures. Each episode typically involves seeking and scheming to find the villain, ending with a dramatic unmasking of the monster. The show focuses on themes of friendship and teamwork. The show originally aired on CBS from 1969 - 1976, but there has been many subseries and reboots since.

We are interested in researching Scoody-Doo IMBD ratings because we all enjoyed Scooby-Doo in our childhoods. We also think that finding certain predictors of animated TV series ratings is useful for the entertainment industry. Specifically, our findings could be useful to anyone looking to create an animated TV series and wanting to know what aspects make up a successful episode. In the paper, "Determining and Evaluating The Most Popular Cartoons Among Children Between 4 and 6 Years of Age" published in 2017, the authors criticize the use of violence, vulgar language, and horror music in Scooby-Doo ([Başal et. al. 2017](https://www.researchgate.net/publication/318108700_Determining_and_Evaluating_The_Most_Popular_Cartoons_Among_Children_Between_4_and_6_Years_of_Age)), yet we can't ignore the huge impact and popularity of Scooby-Doo. In 2013, Scooby-Doo was ranked the fifth greatest cartoon of all time ([TVGuide 2013](https://www.foxnews.com/entertainment/tv-guide-magazines-60-greatest-cartoons-of-all-time)). If Scooby-Doo continues to create spin-off shows, our findings about what makes a successful episode could inform their future episodes as well.

Our primary research question is what factors best explain the variability in the IMBD scores of Scooby-Doo episodes? In other words, what elements tend to contribute to a successful episode? We want to investigate how predictor variables like `monster.amount`, character that unmasks the villain (which we combine into a singular variable, `unmask_villain`), and `network`, adequately explain the variability in IMBD ratings. We hypothesize that episodes with a higher monster count will have a better rating, since we think that there is more action and suspense in episodes with more monsters. We also think that episodes where Fred unmasked the villain will have a higher rating since he is the leader of the group and thus, we think that people will be more drawn to him. Finally, we think that episodes that aired on Cartoon Network will have a better rating, since we think that Cartoon Network has the ability to generate more positive responses since they specialize in cartoons and are pretty well-known. In our analysis, we would like to explore the interaction between these variables as well.

## Data

This Scooby-Doo data was found on the [TidyTuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-13/readme.md#scooby-doo-episodes) database on Github. The data originally comes from [Kaggle](https://www.kaggle.com/datasets/williamschooleman/scoobydoo-complete) and was manually aggregated by user [Plummye](https://www.kaggle.com/williamschooleman) in 2021. The curator took roughly one year to watch every Scooby-Doo iteration and track every variable in this dataset. It is noted that some of the values are subjective by nature of watching, but the original data data curator tried to keep the data collection consistent across the different episodes.

Each observation represents an episode from a rendition of the Scooby-Doo franchise up until February 25, 2021, including movies and specials. The variables that were measured include the series and episode name (which we will not use as predictor variables), network aired on, IMDB score, engagement (represented by number of reviews on IMDB), and many details about what happened in each episode, such as how many monsters appeared, which character captured and unmasked the monster, the terrain of the episode, and more. There is a mix of both numerical and categorical characteristics.

The unmask variable is in the data as 6 separate columns with each column representing a person, such as `unmask.fred`, `unmask.velma`, etc. Before any of our analysis, we combined these columns into one singular column, `unmask_villain`. We also converted `imdb` from a `character` to a `double` as we want it to be a quantitative value.

Our response variable is `imdb`, while our predictor variables are `unmask_villain`, `monster.amount`, and `network`.

`imdb`: double, represents the score on IMDB

`unmask_villain`: character, represents which character unmasked the villain (if any)

`monster.amount`: double, represents the number of monsters in the episode

`network`: character, represents the network the episode was aired on

```{r cleaning}
#| warning: false
scoobydoo <- mutate(scoobydoo, unmask_villain = 
                           ifelse(unmask.fred == TRUE, "Fred",
                           ifelse(unmask.daphnie == TRUE, "Daphne",
                           ifelse(unmask.velma == TRUE, "Velma",
                           ifelse(unmask.shaggy == TRUE, "Shaggy",
                           ifelse(unmask.scooby == TRUE, "Scooby", 
                           ifelse(unmask.other == TRUE, "Other", "None")))))))

scoobydoo <- scoobydoo |>
  mutate(imdb = as.numeric(imdb))
```

## Exploratory data analysis

```{r response-dist}
#| warning: false
#| message: false

p1 <- scoobydoo |>
  ggplot(aes(x = imdb)) +
  geom_histogram() +
  labs(x = "IMDB score",
       y = "Frequency",
       title = "IMDB Score",
       caption = "Figure 1") +
  theme_minimal()
```

```{r response-stats}
#| include = FALSE

scoobydoo |>
  skim(imdb) |>
  select(-skim_type, -skim_variable, -complete_rate,
         - numeric.hist) |> #remove these columns from output
  print(width = Inf) #print all columns
```

```{r qualpred-dist}
#| warning: false
#| message: false

p2 <- scoobydoo |>
  ggplot(aes(x = monster.amount)) +
  geom_histogram(bins=7) +
  labs(x = "Number of Monsters",
       y = "Frequency",
       title = "Number of Monsters",
       caption = "Figure 2") +
  theme_minimal()
```

```{r qualpred-stats}
#| include = FALSE

scoobydoo |>
  skim(monster.amount) |>
  select(-skim_type, -skim_variable, -complete_rate,
         - numeric.hist) |> #remove these columns from output
  print(width = Inf) #print all columns
```

```{r patchwork}
#| warning: false
#| message: false

p1 | p2
```

Figure 1: The distribution of our response variable IMDB scores, `imdb`, is unimodal and roughly symmetrical. The mean is 7.278 and the standard deviation is 0.732. The minimum is 4.2 and the maximum is 9.6. There does not seem to be any significant outliers.

Figure 2: The distribution of the number of monsters, `monster.amount`, is unimodal and right skewed. The median is 1 monster and the IQR is 1 monster. The minimum is 0 monsters and the maximum is 19 monsters. There are a few episodes with notably high amounts of monsters, with 5 episodes having 13 or more monsters.

```{r unmask-dist}

scoobydoo |>
  ggplot(aes(x = unmask_villain)) +
  geom_bar() +
  coord_flip() +
  labs(x = "Network Aired On",
       y = "Frequency",
       title = "Distribution of Who Unmasked the Villain",
       caption = "Figure 3") +
  theme_minimal()
```

Figure 3: The distribution of who unmasks the villain, `unmask_villain`, shows that in a good majority of the episodes, no one unmasked the villain. However, out of the episodes where a villain was unmasked, Fred and Velma were the main characters that unmasked the villain.

```{r catpred-dist}

scoobydoo |>
  ggplot(aes(x = network)) +
  geom_bar() +
  coord_flip() +
  labs(x = "Network Aired On",
       y = "Frequency",
       title = "Distribution of Network Aired On",
       caption = "Figure 4") +
  theme_minimal()
```

Figure 4: The distribution of the network the episode aired on, `network`, shows that a good majority of the episodes aired on ABC. There were also considerable amounts of episodes that aired on Cartoon Network and Boomerang, while there are also networks that aired very few episodes, such as TBC and Adult Swim.

```{r qual}
#| warning: false

scoobydoo |>
  ggplot(aes(x = monster.amount, y = imdb)) +
  geom_point() +
  labs(x = "Number of Monsters",
       y = "IMDB rating",
       title = "Relationship between Number of Monsters and IMDB Rating",
       caption = "Figure 5") +
  theme_minimal()
```

```{r correlation}
#| include = FALSE

scoobydoo |>
  na.omit(monster.amount) |>
  na.omit(imdb) |>
  summarise(r = cor(monster.amount, imdb)) |> pull()
```

Figure 5: The relationship between the number of monsters and the IMDB score is moderate, negative, and linear. Omitting NULL values in `monster.amount` and `imdb`, the correlation is -0.350. It seems that as the number of monsters increase, the IMDB score tends to decrease, on average. However, as seen earlier, the median of the distribution of the number of monsters is 1, so as we increase the number of monsters, there are less and less observations, which makes the relationship between the two variables hard to observe as the number of monsters increase.

```{r cat2}
#| warning: false
#| message: false

scoobydoo |>
  ggplot(aes(x = unmask_villain, y = imdb)) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "Who Unmasks the Villain",
       y = "IMDB rating",
       title = "Relationship between Who Unmasks the Villain and IMDB Rating",
       caption = "Figure 6"
       ) +
  theme_minimal()
```

Figure 6: From the distribution of the different boxplots for each character included in `unmask_villain`, we observe that many of the interquartile intervals of the boxplots overlap, meaning that their IMDB ratings are quite similar. Since they all overlap, we should consider whether this variable is important for our model.

```{r cat}
#| warning: false
#| message: false

scoobydoo |>
  ggplot(aes(x = network, y = imdb)) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "Network Aired On",
       y = "IMDB rating",
       title = "Relationship between Network Aired On and IMDB Rating",
       caption = "Figure 7"
       ) +
  theme_minimal()
```

Figure 7: From the distribution of the different boxplots for each network, we observe that many of the interquartile intervals of the boxplots overlap, meaning that their IMDB ratings are quite similar. It seems that Cartoon Network generally received the best ratings, while Warner Bros. Picture and The CW generally received the worst ratings. We also observe a few outliers in the distribution of IMDB ratings for some networks, such as Warner Home Video and ABC. Many of the networks have IMDB ratings that are pretty symmetrical, as the line representing the median is close to the middle of the box, such as in the case of CBS and The CW, but some are pretty skewed, such as in the case of Syndication, The WB, and Warner Bros. Picture.

# Methodology:

Since our response variable is quantitative, we decided to use multiple linear regression for modeling. We also split our original data set into a training (75%) and testing (25%) set to attempt to prevent model overfitting. The predictor variables we were interested in were `network`, `monster.amount`, and `unmask_villain`. From our initial exploratory data analysis, we saw a lot of variation within the relationship between network and IMDB, so we wanted to include `network` as part of our model. The relationships between `monster.amount` and `unmask_villain` each with IMDB seemed less strong, but since we are interested in how these predictor variables affect IMDB as well as any interaction effects that could be made within the three variables, we included these two variables in our model as well. To compare our models, we plan on using 3-fold cross validation, and we also included a function to calculate adjusted R squared, AIC, and BIC, which we will use when choosing our final model.

For each model, we decided to create a recipe, where we performed these steps across all models:

1.  Simplified the number of networks in `networks` by using step_other with a threshold of 30.
2.  Created dummy variables for all nominal predictors using step_dummy.
3.  Removed predictors with zero variance using step_zv.

We tested a total of four different models. Since we knew that we wanted to include the variables, `network`, `monster.amount`, and `unmask_villain`, we tested different interactions between combinations of two of the three predictor variables.

Model 1: imdb \~ network + monster.amount + unmask_villain with no interaction terms

Model 2: imdb \~ network + monster.amount + unmask_villain with interaction between monster.amount and unmask_villain

Model 3: imdb \~ network + monster.amount + unmask_villain with interaction between monster.amount and network

Model 4: imdb \~ network + monster.amount + unmask_villain with interaction between unmask_villain and network

```{r function}
calc_model_stats <- function(x) {
  glance(extract_fit_parsnip(x)) |>
    select (adj.r.squared, AIC, BIC)
}
```

```{r}
#| label: split

set.seed(6)
data_split <- initial_split(scoobydoo, prop = 0.75)
train_data <- training(data_split)
test_data <- testing(data_split)

set.seed(6)
folds <- vfold_cv(train_data, v = 3)

model_spec <- linear_reg() |>
  set_engine("lm")
```

```{r}
#| label: recipe2

recipe_2 <- recipe(imdb ~ network + monster.amount + unmask_villain,
                    data = train_data) |>
  step_other(network, threshold = 30) |>
  step_interact(terms = ~ monster.amount:unmask_villain) |>
  step_dummy(all_nominal_predictors()) |>
  step_zv(all_predictors())

wflow2 <- workflow() |>
  add_model(model_spec) |>
  add_recipe(recipe_2)
```

```{r}
#| label: recipe3

recipe_3 <- recipe(imdb ~ network + monster.amount + unmask_villain,
                    data = train_data) |>
  step_other(network, threshold = 30) |>
  step_interact(terms = ~ monster.amount:network) |>
  step_dummy(all_nominal_predictors()) |>
  step_zv(all_predictors())

wflow3 <- workflow() |>
  add_model(model_spec) |>
  add_recipe(recipe_3)
```

```{r}
#| label: recipe1

recipe_1 <- recipe(imdb ~ network + monster.amount + unmask_villain,
                    data = train_data) |>
  step_other(network, threshold = 30) |>
  step_dummy(all_nominal_predictors()) |>
  step_zv(all_predictors())

wflow1 <- workflow() |>
  add_model(model_spec) |>
  add_recipe(recipe_1)
```

```{r}
#| label: recipe4

recipe_4 <- recipe(imdb ~ network + monster.amount + unmask_villain,
                    data = train_data) |>
  step_other(network, threshold = 30) |>
  step_interact(terms = ~ unmask_villain:network) |>
  step_dummy(all_nominal_predictors()) |>
  step_zv(all_predictors())

wflow4 <- workflow() |>
  add_model(model_spec) |>
  add_recipe(recipe_4)
```

```{r results='hide'}
#| label: fit

fit_rs1 <- wflow1 |>
  fit_resamples(resamples=folds,
                control = control_resamples(extract = calc_model_stats))

fit_rs2 <- wflow2 |>
  fit_resamples(resamples=folds,
                control = control_resamples(extract = calc_model_stats))

fit_rs3 <- wflow3 |>
  fit_resamples(resamples=folds,
                control = control_resamples(extract = calc_model_stats))

fit_rs4 <- wflow4 |>
  fit_resamples(resamples=folds,
                control = control_resamples(extract = calc_model_stats))

map_df (fit_rs1$.extracts, ~ .x[[1]] [[1]]) |>
  summarise (mean_adj_rsq = mean(adj.r.squared),
             mean_aic = mean(AIC),
             mean_bic = mean (BIC)) |>
  kable(digits = 3, caption = "wflow1")

map_df (fit_rs2$.extracts, ~ .x[[1]] [[1]]) |>
  summarise (mean_adj_rsq = mean(adj.r.squared),
             mean_aic = mean(AIC),
             mean_bic = mean (BIC)) |>
  kable(digits = 3, caption = "wflow2")

map_df (fit_rs3$.extracts, ~ .x[[1]] [[1]]) |>
  summarise (mean_adj_rsq = mean(adj.r.squared),
             mean_aic = mean(AIC),
             mean_bic = mean (BIC)) |>
  kable(digits = 3, caption = "wflow3")

map_df (fit_rs4$.extracts, ~ .x[[1]] [[1]]) |>
  summarise (mean_adj_rsq = mean(adj.r.squared),
             mean_aic = mean(AIC),
             mean_bic = mean (BIC)) |>
  kable(digits = 3, caption = "wflow4")
```

| Model \# | Mean Adjusted R-Squared | Mean AIC | Mean BIC |
|----------|-------------------------|----------|----------|
| 1        | 0.269                   | 610.982  | 676.177  |
| 2        | 0.333                   | 580.208  | 633.100  |
| 3        | 0.265                   | 606.73   | 649.782  |
| 4        | 0.303                   | 603.144  | 694.162  |

From these statistics, it is clear that Model #2 (imdb \~ network + monster.amount + unmask_villain with interaction between monster.amount and unmask_villain) had the highest mean adjusted R-squared and the lowest AIC and BIC values. Therefore, we will use this model as our final model.

# Results:

```{r finalmodel}

scooby_fit <- wflow2 |>
  fit(data = train_data)

tidy(scooby_fit) |>
  kable(digits=3)
```

```{r predictions}

train_pred <- predict(scooby_fit, train_data) |>
  bind_cols(train_data)

test_pred <- predict(scooby_fit, test_data) |>
  bind_cols(test_data)
```

```{r rsqrmse}

rsq_train <- rsq(train_pred, truth = imdb, estimate = .pred)
rsq_test <- rsq(test_pred, truth = imdb, estimate = .pred)

rmse_train <- rmse(train_pred, truth = imdb, estimate = .pred)
rmse_test <- rmse(test_pred, truth = imdb, estimate = .pred)
```

This is the model output for our final model, where we predicted `imdb` with `network`+ `monster.amount` + `unmask_villain` with an interaction between `monster.amount` and `unmask_villain`. From the p-values of the coefficients, we see that 8 of 18 predictor variables have significant values when using a threshold of 0.05. Most of the low p-values in coefficients come from `network`. It is interesting that `monster.amount_x_unmask_villainVelma` was significant while none of the other interactions were. Another significant coefficient value that is worthy to note is `unmask_villain_None`. From our earlier EDA, we did see that 'None' was the largest category for `unmask_villain`, so it is possible the coefficient value is significant only because there was a large amount of data for it.

| Dataset  | R-Squared | RMSE  |
|----------|-----------|-------|
| Training | 0.483     | 0.554 |
| Testing  | 0.506     | 0.423 |

The model's R-squared value on the training data is approximately 0.483, which means that approximately 48.3 percent of the variation in the response variable explained by our regression model. However, the model's R-squared value on the testing data is approximately 0.506, which is actually surprisingly higher than the value for our training data. Since the R-squared values are relatively close, we are not too concerned about our model having overfit the data. The same trend is observed in our RMSE values, as the RMSE for the training data is 0.554, while it is 0.423 for the testing data.

All in all, from our model, we see that `network` and `monster.amount` seem to be significant when predicting IMDB scores for different Scooby-Doo episodes. We observe that the variable, `unmask_villain`, as well as the interaction of it with `monster.amount` carry very few significant coefficients, so we may reconsider including this variable as a predictor variable in future models. However, for this project, since we were especially interested in using `unmask_villain` as a predictor variable, we retain it in our final model.

::: callout-important
Before you submit, make sure your code chunks are turned off with `echo: false` and there are no warnings or messages with `warning: false` and `message: false` in the YAML.
:::
