---
title: "Analyzing IMBD Scores of Scooby-Doo Episodes"
author: "Regression Rockstars: James Cai, Steph Reinke, Sarah Wu, Michael Zhou"
date: "November 16, 2023"
format: pdf
execute: 
  warning: false
  message: false
  echo: false
editor: visual
---

```{r}
#| label: load-pkg-data
#| warning: false
#| message: false

library(tidyverse)
library(tidymodels)
library(knitr) 
library(patchwork)
library(skimr)

scoobydoo <- read_csv("data/Scooby-Doo Completed.csv")
```

# Introduction and Data:

## Introduction

Scooby-Doo is a popular animated TV show that follows a group of teenagers and a talking Great Dane, Scooby-Doo, as they solve mysteries involving supernatural monsters and creatures. Each episode typically involves seeking and scheming to find the villain, ending with a dramatic unmasking of the monster. The show focuses on themes of friendship and teamwork. The show originally aired on CBS from 1969 - 1976, but there has been many subseries and reboots since.

We are interested in researching Scoody-Doo IMBD ratings because we all enjoyed Scooby-Doo in our childhoods. We also think that finding certain predictors of animated TV series ratings is useful for the entertainment industry. Specifically, our findings could be useful to anyone looking to create an animated TV series and wanting to know what aspects make up a successful episode. In the paper, "Determining and Evaluating The Most Popular Cartoons Among Children Between 4 and 6 Years of Age" published in 2017, the authors criticize the use of violence, vulgar language, and horror music in Scooby-Doo ([Başal et. al. 2017](https://www.researchgate.net/publication/318108700_Determining_and_Evaluating_The_Most_Popular_Cartoons_Among_Children_Between_4_and_6_Years_of_Age)), yet we can't ignore the huge impact and popularity of Scooby-Doo. In 2013, Scooby-Doo was ranked the fifth greatest cartoon of all time ([TVGuide 2013](https://www.foxnews.com/entertainment/tv-guide-magazines-60-greatest-cartoons-of-all-time)). If Scooby-Doo continues to create spin-off shows, our findings about what makes a successful episode could inform their future episodes as well.

Our primary research question is what factors best explain the variability in the IMBD scores of Scooby-Doo episodes? In other words, what elements tend to contribute to a successful episode? We want to investigate how predictor variables like `monster.amount`, `engagement`, character that unmasks the villain (`unmask.fred`, and such for all five characters part of the main group), `network`, and more, adequately explain the variability in IMBD ratings. We hypothesize that episodes with a higher monster count will have a better rating, since we think that there is more action and suspense in episodes with more monsters. We also hypothesize that the higher engagement, the worse the rating will be. This is because we think that people are more likely to write a review online when they dislike the episode rather than if they liked the episode. We think that episodes where Fred unmasked the villain will have a higher rating since he is the leader of the group and thus, we think that people will be more drawn to him. Finally, we think that episodes that aired on Cartoon Network will have a better rating, since we think that Cartoon Network has the ability to generate more positive responses since they specialize in cartoons and are pretty well-known. In our analysis, we would like to explore the interaction between these variables as well as consider other predictors in the dataset.

## Data

This Scooby-Doo data was found on the [TidyTuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-13/readme.md#scooby-doo-episodes) database on Github. The data originally comes from [Kaggle](https://www.kaggle.com/datasets/williamschooleman/scoobydoo-complete) and was manually aggregated by user [Plummye](https://www.kaggle.com/williamschooleman) in 2021. The curator took roughly one year to watch every Scooby-Doo iteration and track every variable in this dataset. It is noted that some of the values are subjective by nature of watching, but the original data data curator tried to keep the data collection consistent across the different episodes.

Each observation represents an episode from a rendition of the Scooby-Doo franchise up until February 25, 2021, including movies and specials. The variables that were measured include the series and episode name (which we will not use as predictor variables), network aired on, IMDB score, engagement (represented by number of reviews on IMDB), and many details about what happened in each episode, such as how many monsters appeared, which character captured and unmasked the monster, the terrain of the episode, and more. There is a mix of both numerical and categorical characteristics.

## Initial exploratory data analysis

```{r response-dist}
#| warning: false
#| message: false

scoobydoo <- scoobydoo |>
  mutate(imdb = as.numeric(imdb))

p1 <- scoobydoo |>
  ggplot(aes(x = imdb)) +
  geom_histogram() +
  labs(x = "IMDB score",
       y = "Frequency",
       title = "IMDB Score",
       caption = "Figure 1") +
  theme_minimal()
```

```{r response-stats}
#| include = FALSE

scoobydoo |>
  skim(imdb) |>
  select(-skim_type, -skim_variable, -complete_rate,
         - numeric.hist) |> #remove these columns from output
  print(width = Inf) #print all columns
```

```{r qualpred-dist}
#| warning: false
#| message: false

p2 <- scoobydoo |>
  ggplot(aes(x = monster.amount)) +
  geom_histogram(bins=7) +
  labs(x = "Number of Monsters",
       y = "Frequency",
       title = "Number of Monsters",
       caption = "Figure 2") +
  theme_minimal()
```

```{r qualpred-stats}
#| include = FALSE

scoobydoo |>
  skim(monster.amount) |>
  select(-skim_type, -skim_variable, -complete_rate,
         - numeric.hist) |> #remove these columns from output
  print(width = Inf) #print all columns
```

```{r patchwork, out.width = "70%"}
#| warning: false
#| message: false

p1 | p2
```

Figure 1: The distribution of our response variable IMDB scores, `imdb`, is unimodal and roughly symmetrical. The mean is 7.278 and the standard deviation is 0.732. The minimum is 4.2 and the maximum is 9.6. There does not seem to be any significant outliers.

Figure 2: The distribution of the number of monsters, `monster.amount`, is unimodal and right skewed. The median is 1 monster and the IQR is 1 monster. The minimum is 0 monsters and the maximum is 19 monsters. There are a few episodes with notably high amounts of monsters, with 5 episodes having 13 or more monsters.

```{r catpred-dist, out.width = "70%"}

scoobydoo |>
  ggplot(aes(x = network)) +
  geom_bar() +
  coord_flip() +
  labs(x = "Network Aired On",
       y = "Frequency",
       title = "Distribution of Network Aired On",
       caption = "Figure 3") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Figure 3: The distribution of the network the episode aired on, `network`, shows that a good majority of the episodes aired on ABC. There were also considerable amounts of episodes that aired on Cartoon Network and Boomerang, while there are also networks that aired very few episodes, such as TBC and Adult Swim.

```{r qual, out.width = "70%"}
#| warning: false

scoobydoo |>
  ggplot(aes(x = monster.amount, y = imdb)) +
  geom_point() +
  labs(x = "Number of Monsters",
       y = "IMDB rating",
       title = "Relationship between Number of Monsters and IMDB Rating",
       caption = "Figure 4") +
  theme_minimal()
```

```{r correlation}
#| include = FALSE

scoobydoo |>
  na.omit(monster.amount) |>
  na.omit(imdb) |>
  summarise(r = cor(monster.amount, imdb)) |> pull()
```

Figure 4: The relationship between the number of monsters and the IMDB score is moderate, negative, and linear. Omitting NULL values in `monster.amount` and `imdb`, the correlation is -0.350. It seems that as the number of monsters increase, the IMDB score tends to decrease, on average. However, as seen earlier, the median of the distribution of the number of monsters is 1, so as we increase the number of monsters, there are less and less observations, which makes the relationship between the two variables hard to observe as the number of monsters increase.

```{r cat, out.width = "70%"}
#| warning: false
#| message: false

scoobydoo |>
  ggplot(aes(x = network, y = imdb)) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "Network Aired On",
       y = "IMDB rating",
       title = "Relationship between Network Aired On and IMDB Rating",
       caption = "Figure 5"
       ) +
  theme_minimal()
```

Figure 5: From the distribution of the different boxplots for each network, we observe that many of the interquartile intervals of the boxplots overlap, meaning that their IMDB ratings are quite similar. It seems that Cartoon Network generally received the best ratings, while Warner Bros. Picture and The CW generally received the worst ratings. We also observe a few outliers in the distribution of IMDB ratings for some networks, such as Warner Home Video and ABC. Many of the networks have IMDB ratings that are pretty symmetrical, as the line representing the median is close to the middle of the box, such as in the case of CBS and The CW, but some are pretty skewed, such as in the case of Syndication, The WB, and Warner Bros. Picture.

```{r interact, out.width = "65%"}
#| warning: false

scoobydoo |>
  ggplot(aes(x = monster.amount, y = imdb, color = network)) +
  geom_point() +
  labs(x = "Number of Monsters",
       y = "IMDB rating",
       title = "Relationship between Number of Monsters and IMDB Rating",
       subtitle = "Colored by Network Aired On",
       color = "Network Aired On",
       caption = "Figure 6") +
  theme_minimal()
```

Figure 6: In particular, we tried to see if we could find signs of interactions between the number of monsters in an episode and the network that the episode aired on. For example, were there any networks that particularly included more monsters or less monsters in each episode, and how did this affect the IMDB rating? From the scatterplot, it seems that The CW, in particular, included a higher amount of monsters in each episode, but these episodes did not receive the highest ratings and the ratings were pretty consistent throughout. Boomerang seemed to have many episodes with 1 monster and these episodes received a range of ratings from around 6 to 9. CBS seemed to have the most success when it limited the number of monsters to 2. We are interested in further exploring this interaction in our analysis.

# Methodology:

# Results:

::: callout-important
Before you submit, make sure your code chunks are turned off with `echo: false` and there are no warnings or messages with `warning: false` and `message: false` in the YAML.
:::
